\documentclass[a4paper,12pt]{article}
\usepackage[english,vietnamese]{babel}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage[nottoc,numbib]{tocbibind}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}
\setcounter{page}{0}
\thispagestyle{empty}
\vspace*{\stretch{1}}
\begin{flushright}
  \setlength{\baselineskip}{1.4\baselineskip}
\textbf{\Huge Python Package\\Metadata Management}
  \noindent\rule{\textwidth}{5pt}
  \emph{\Large Basic Databases}
  \vspace{\stretch{1}}

  \textbf{by Nguyễn Gia Phong, Nguyễn Quốc Thông,\\
          Nguyễn Văn Tùng and Trần Minh Vương\\}
  \selectlanguage{english}
  \today
\end{flushright}
\vspace*{\stretch{2}}
\pagebreak

\selectlanguage{english}
\tableofcontents
\pagebreak

\section{Introduction}
\subsection{Brief Description}
In traditional Unix-like operating systems like GNU/Linux distributions
and BSD-based OSes, package managers tries to synchronize the packages metadata
(such as available versions and dependencies) with that of central repositories.
While this proves to be reliable and efficient, language-specific
package managers do not usually have such synchronized databases,
since they focus on development libraries which have more flexible contraints.

Within the Python packaging ecosystem, this is the case, where package managers
like \verb|pip| needs to fetch metadata of each package to be installed
to find out dependencies and other information.  This turns out to have heavy
performance penalty on the dependency resolution process alone, which is
already a NP-hard problem.  This project explores ways to store these metadata
in an efficient in a database, to be used in practice either locally or in a
local/regional network, to avoid Python package managers from having to
fetch (and potentially build) entire packages just to find out if it conflicts
with others.

\selectlanguage{vietnamese}
\subsection{Authors and Credits}
The work has been undertaken by group number 8, whose members are listed
in the following table.
\begin{center}
  \begin{tabular}{c c}
    \toprule
    Full name & Student ID\\
    \midrule
    Nguyễn Gia Phong & BI9-184\\
    Nguyễn Quốc Thông & BI9-214\\
    Nguyễn Văn Tùng & BI9-229\\
    Trần Minh Vương & BI9-239\\
    \bottomrule
  \end{tabular}
\end{center}

This report is licensed under a CC BY-SA 4.0 license, while the source code is
available on GitHub\footnote{\url{https://github.com/McSinyx/cheese-shop}}
under AGPLv3+.

We would like to express our special thanks to Dr. Nguyễn Hoàng Hà,
whose lectures gave us basic understanding on the key principles of
relational databases.  In addition, we also recieved a lot of help from
the Python packaging community over \#pypa on Freenode on understanding
the structure of the metadata as well as finding a way to fetch these
data from package indices.

\newpage
\selectlanguage{english}
\section{User Requirements}

\section{Data Definition}
\subsection{Entity Relationship Diagram}
\subsection{Database Schema}

\section{Data Query}

\section{Conclusion}

\begin{thebibliography}{69}
\end{thebibliography}
\end{document}
